### 2013-06-18 ms_V3.tex

Current global changes make it important to be able to predict which
interactions will occur in emerging ecosystems. Most of the current methods to
infer the existence of interactions between two species require a good knowledge
of their behaviour or a direct observation of interactions. In this paper, we
overcome these limitations by developing a method, inspired from the niche model
of food web structure, using the statistical relationship between predator and
prey body size to infer the matrix of potential interactions among a pool of
species.  The novelty of our approach is to infer, for any species of a given
species pool, the three species specific parameters of the niche model. It
allows one to evaluate the feeding interactions of a new species entering the
community. We find that this method gives robust predictions of the structure of
food webs, and that its efficiency is increased when the strength of the body-
size relationship between predators and preys increases. We finally illustrate
the potential of the method to infer the metaweb structure of pelagic fishes of
the Meditarrannean sea under different global change scenarios.

@@

Inferring potential interactions among species of an arbitrary defined pool is a major step to predict the structure of emergent communities and their functioning. We call these potential interactions among species from a regional pool the \emph{metaweb} \parencite{Dunne2006}. A metaweb takes the form of an adjacency matrix $\mathbf{MW}$, of size $s\times s$ for a pool of $s$ species, and in which $\mathbf{MW_{ij}} = 1$ if species $i$ can consume species $j$, and $0$ otherwise. This matrix aggregates the trophic interactions among all species from the pool that are susceptible to both co-occur and interact at the regional scale \parencite{Dunne2006}. With a metaweb in hands, one could analyze the impacts of global changes, such as range shifts or species invasions, on the potential community structure, by extracting the relevant species and examining the properties of the community they define. While this concept is progressively finding its way through theoretical spatial food web ecology \parencite{Lafferty2010, Pillai2009, Gravel2011a, Gravel2011b}, it is still limited by data availability and predictive accuracy. Published metaweb data rely on literature surveys \parencite{Havens1992, Piechnik2008, Baiser2012}, or a compilation of several local food webs \parencite{Stanko2002, Poisot2012a}, making them resolved only for species that co-occurred a large enough number of times.

@@

In this paper, we present a method designed to infer the potential interactions between all pairs of species of a species pool (the metaweb) based on observations of body size of predators and their prey. We do so by a parameterization of the niche model, based on the well-documented allometric scaling relationship between predator and prey \parencite{Cohen2003, Brose2006, Riede2010}. We first develop the method and apply it to food webs from various environments. We find the method accurately predicts the interactions (and lack thereof), and that the accuracy increases with the strength of the predator-prey body size relationship. We then analyze the sensitivity of the method to incomplete data (missing links) and find that it is robust to sampling effort. We finally illustrate the potential of the method to infer the metaweb structure of pelagic fishes of the Meditarrannean sea and the consequences of alteration of body size distribution by global changes or anthropic forcings.

@@

Assuming that body size is the main niche axis structuring trophic interactions,
the parameter $n_i$ corresponds simply to the log of body size (in mass or
length) of species $i$. Though only the relative position of all species along
the body size gradient needs to be respected, it is possible to standardize log
body size values between 0 (minimum size in the regional species pool) and 1
(maximal size). We then consider a linear relationship between the decimal
logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
This relationship is obtained by fitting the linear model $c =
\mathrm{log}_{10}(M_{prey})=\alpha_0 +
\alpha_1\times\mathrm{log}_{10}(M_{pred})$ to the data, where $M_{prey}$ and
$M_{pred}$ are the prey and predator body size respectively. The lower and upper
boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
quantile regressions between $\mathrm{log}_{10}(M_{prey})$ and
$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum,
the parameter $n_i$ for any species of the metaweb is given by the standardized
value of the log body size $M_i$, $c_i$ is estimated from the linear regression
between predator and prey log body size and $r_i$ from the quantile regressions.

@@

The parameterized niche model tends to overestimate the number of links in a web (see the example at Fig. 2). This result is significant but not surprising, given that these datasets do not necessarily contain all links, as they were not designed with this purpose, and thus some of the links might have been missed. This interpretation is also reminiscent of previous debates on the difficulty to sample all links in a web \parencite{Martinez1999}. It is also well known that the niche model predicts a continuous diet along the niche axis (the webs are said to be interval \parencite{Cohen1990, Stouffer2006}), while real food webs do not have this characteristic. We thus might over predict link density within the niche of a given species. Previous studies \parencite{Allesina2008} and the Application 1 however show this problem is easily circumvented when a second niche axis, \emph{e.g.} an environmental niche, comes into play. A recent study on dimensionality of networks shown that most webs have between 3 and 7 dimensions \parencite{Eklof2013}, meaning that adding a few more niche axes can greatly improve the accuracy of predictions.

@@

@@

Our application with the Mediterannean pelagic fish food web provides an example of how straightforward it is to add additional information so as to improve the parameterization. A similar approach could also build on the comptability of other traits such as phenology, location in the water column or hunting modes. While the approach we describe here is based on very simple statistics, the next methodological efforts will also have to take into account more various and heterogeneous sources of data such as phylogeny \parencite{Eklof2012} and expert knowledge. Bayesian inference appears a good candidate to achieve this goal with the possibility to constrain the prior distribution of parameters for each species.

@@

\section{Acknowledgements}
We thank I. Gounand for preparing the food web data. DG received financial support from NSERC and Canada Research Chair program. TP is funded by a MELS-FQRNT post-doctoral fellowship.
\newpage

>>>>

Current global changes make it important to be able to predict which
interactions will occur in emerging ecosystems. Most of the current methods to
infer the existence of interactions between two species require a good knowledge
of their behaviour or a direct observation of interactions. In this paper, we
overcome these limitations by developing a method, inspired from the niche model
of food web structure, using the statistical relationship between predator and
prey body size to infer the matrix of potential interactions among a pool of
species. The novelty of our approach is to infer, for any species of a given
species pool, the three species specific parameters of the niche model. The
method applies to both local and metaweb scales. It allows one to evaluate the
feeding interactions of a new species entering the community. We find that this
method gives robust predictions of the structure of food webs, and that its
efficiency is increased when the strength of the body- size relationship between
predators and preys increases. We finally illustrate the potential of the method
to infer the metaweb structure of pelagic fishes of the Meditarrannean sea under
different global change scenarios.

@@

Inferring potential interactions among species of an arbitrary defined pool is a
major step to predict the structure of emergent communities and their
functioning. We call these potential interactions among a given set of species, wether
at the local or regional scales, the \emph{metaweb} \parencite{Dunne2006}. A
metaweb takes the form of an adjacency matrix $\mathbf{MW}$, of size $s\times s$
for a pool of $s$ species, and in which $\mathbf{MW_{ij}} = 1$ if species $i$
can consume species $j$, and $0$ otherwise. This matrix aggregates the trophic
interactions among all species from the pool that are susceptible to both
co-occur and interact at the regional scale \parencite{Dunne2006}. With a
metaweb in hands, one could analyze the impacts of global changes, such as range
shifts or species invasions, on the potential community structure, by extracting
the relevant species and examining the properties of the community they define.
While this concept is progressively finding its way through theoretical spatial
food web ecology \parencite{Lafferty2010, Pillai2009, Gravel2011a, Gravel2011b},
it is still limited by data availability and predictive accuracy. Published
metaweb data rely on literature surveys \parencite{Havens1992, Piechnik2008,
Baiser2012}, or a compilation of several local food webs \parencite{Stanko2002,
Poisot2012a}, making them resolved only for species that co-occurred a large
enough number of times.

@@

In this paper, we present a method designed to infer the potential interactions
between all pairs of species of a species pool based on observations of body
size of predators and their prey. The method applies to both the local and the
metaweb scales. We do so by a parameterization of the niche model, based on the
well-documented allometric scaling relationship between predator and prey
\parencite{Cohen2003, Brose2006, Riede2010}. We first develop the method and
apply it to food webs from various environments. We find the method accurately
predicts the interactions (and lack thereof), and that the accuracy increases
with the strength of the predator-prey body size relationship. We then analyze
the sensitivity of the method to incomplete data (missing links) and find that
it is robust to sampling effort. We finally illustrate the potential of the
method to infer the metaweb structure of pelagic fishes of the Meditarrannean
sea and the consequences of alteration of body size distribution by global
changes or anthropic forcings. The method is best suited for strongly
size-structured food webs and will likely not hold for other types of
non-body-size structured interactions. We therefore conclude on the future
issues to generalize this approach to other types of trait matching models.

@@

Assuming that body size is the main niche axis structuring trophic interactions,
the parameter $n_i$ corresponds simply to the log of body size (in mass or
length) of species $i$. Though only the relative position of all species along
the body size gradient needs to be respected, it is possible to standardize log
body size values between 0 (minimum size in the regional species pool) and 1
(maximal size). We then consider a linear relationship between the decimal
logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
This relationship is obtained by fitting the linear model $c =
\mathrm{log}_{10}(M_{prey})=\alpha_0 +
\alpha_1\times\mathrm{log}_{10}(M_{pred})$ to the data, where $M_{prey}$ and
$M_{pred}$ are the prey and predator body size respectively. The lower and upper
boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
quantile regressions between $\mathrm{log}_{10}(M_{prey})$ and
$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at
Fig. 2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
corresponding parameters of the linear quantile regresions are
$\beta_{0,low/high}$ and $\beta_{1,low/high}$. In sum, the parameter $n_i$ for
any species of the metaweb is given by the standardized value of the log body
size $M_i$, $c_i$ is estimated from the linear regression between predator and
prey log body size and $r_i$ from the quantile regressions. Type I regressions
were used because there is no equivalence of type II models for quantile
regressions.

@@

The parameterized niche model tends to overestimate the number of links in a web
(see the example at Fig. 2). This result is significant but not surprising,
given that these datasets do not necessarily contain all links, as they were not
designed with this purpose, and thus some of the links might have been missed.
This interpretation is also reminiscent of previous debates on the difficulty to
sample all links in a web \parencite{Martinez1999}. It is also well known that
the niche model predicts a continuous diet along the niche axis (the webs are
said to be interval \parencite{Cohen1990, Stouffer2006}), while real food webs
do not have this characteristic. We thus might over predict link density within
the niche of a given species. Previous studies \parencite{Allesina2008} and the
Application 1 however show this problem is easily circumvented when a second
niche axis, \emph{e.g.} an environmental niche, comes into play. A recent study
on dimensionality of networks shown that most webs have between 3 and 6
dimensions \parencite{Eklof2013}, meaning that adding a few more niche axes can
greatly improve the accuracy of predictions.

@@

It appears at Fig. 2 that the feeding range increases with the body size of the
predator. This result was quite general across datasets with a good fit of the
predator-prey body size relationship, although with considerable variation in
the slope of the relationship. It offers the possibility to compare empirical
based estimates of the parameters to the original niche model of
\textcite{Williams2000}. For this specific dataset that the model for the
centroid is $c_i = -1.34 + 0.66n_i$ and the average range
($\overline{r}_i=(r_{high,i} - r_{low,i})/2$) is $\overline{r}_i = 0.63 +
0.78n_i$. The original niche models assumed that $r_i$ scales linearly with
connectance $C$ and the niche position, such that $r_i = 2Cn_i$. Even though the
parameterization suggests a linear increase of generality with body size, the
final number of preys in the diet for a given size will depend on the frequency
distribution of body size. A large predator for instance could have a large
feeding range, but only few species to find on and effectively appears as a
specialist. This relationship will have to be investigated further, among
several food webs (e.g. \textcite{Digel2011}), because the scaling of generality
with trophic rank has several consequences on persistence
\parencite{Gravel2011b} and food web dynamics \parencite{Brose2006,Berlow2009}.

@@

Our application with the Mediterannean pelagic fish food web provides an example
of how straightforward it is to add additional information so as to improve the
parameterization. A similar approach could also build on the comptability of
other traits such as phenology, location in the water column or hunting modes.
While the approach we describe here is based on very simple statistics, the next
methodological efforts will also have to take into account more various and
heterogeneous sources of data such as phylogeny \parencite{Eklof2012} and expert
knowledge. Bayesian inference appears a good candidate to achieve goal. It
offers the possibility to constrain the prior distribution of the likelihood of
any pairwise interaction, based on trait matching, using alternative source of
data. The method we employed here was based on the match between predator and
prey traits. This method could be generalized by looking at the match between
all potential traits. \textcite{Eklof2013} indeed found that the match between
only three traits is enough to encompass a vast majority of interactions. But
when such data is not always available, then it might be possible to use
phylogeny as a proxy for a high dimensional trait species, provided that traits
are conserved along the phylogeny \parencite{Mouquet2012}. A bayesian addition
to the model would be to weight the likelihood that species $j$ is a predator of
species $i$, considering that the closest relative of this predator is also a
predator of $i$. It could account for part of the unexplained variation we found
in our analysis, for instance by constraining the range of the diet for some
large predators or by creating holes within the feeding range
\parencite{Rall2011}.

@@

\section{Acknowledgements}
We thank I. Gounand for preparing the food web data. We also thank N. Martinez,
U. Brose and two anonymous reviewers for their constructive comments and
stimulating discussion. DG received financial support from NSERC and Canada
Research Chair program. TP is funded by a MELS-FQRNT post-doctoral fellowship.
\newpage

### 2013-06-18 replies.tex

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{As stated
in the abstract, our method allows to ``infer the matrix of potential
interactions among a pool of species'', and does so regardless of whether one is
working at the local or regional scale. In the text, we give examples at both
these scales (locally in figures 2 and 3, regionnaly in figure 5). We do agree
with the fact that additional information will make the predictions better; this
is described at length in the text, and an example of this (including
co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
explicitely written in the discussion (L. XXX-XXX).}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We agree
that the fit of the model is only as strong as the relationship between prey and
predator body-size. This is the purpose of Fig. 3; this relationship is also
described in section 3.1 ``Predictive performance''.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of Rohr et al. (2010), does not allow to evaluate the parameters of a new species entering the community, neither the metaweb (which is the object of the current study). It is therefore not possible to infer the potential links an immigrating species will do with the resident species. These methods also require a complete knowledge of the interactions in the community. Our method is consequently much more robust than previous methods to infer the parameters of the niche model. Based on these arguments, we believe that the method  will be used for instance to study the interactions in emerging communities following global changes.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
correct prediction of absence or presence of an interaction is the most
interesting part of a model is ultimately a matter of personal taste, and
adequation to the study objectives. Given that (especialyl when no other traits
than body size are included), this method tends to over-estimate the number of
links, we argue that correctly predicting absences of links is an extremely
important feature.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%. }}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The fact that our
model over-predict the number of interactions is abundantly discussed in the
manuscript (along with why, and how to overcome it), so we will not elaborate
further on it in this reply. In the original niche model paper, it is true
that $c$ is not constrained by $n$. However, the purposes of the two models are
not the same. The niche model allows to generate a distribution of network
properties based only on connectance and richness. We add allometric
informations so as to be able to estimate species-level interactions in addition
to network properties. The allometric relationshipss on which we rely are well
documented. As for the fact that other traits can be added, this is discussed in
the manuscript at several places, including a whole figure. We made no changes
to the manuscript.}}

>>>>

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that using phylogenetic information should help improve the technique much beyond what we actually do. This is why we made a mention of this opportunity toward the end of the discussion. But it's right we only mentionned it and did not developped our ideas any further. We added the following lines (LXXX) to the discussion:}}

\textcolor{blue}{Bayesian inference appears a good candidate to achieve goal. It offers the possibility to constrain the prior distribution of the likelihood of any pairwise interaction, based on trait matching, using alternative source of data. The method we employed here was based on the match between predator and prey traits. This method could be generalized by looking at the match between all potential traits. Eklof et al. (2013) indeed found that the match between only three traits is enough to encompass a vast majority of interactions. But when such data is not always available, then it might be possible to use phylogeny as a proxy for a high dimensional trait species, provided that traits are conserved along the phylogeny (Mouquet et al. 2012). A bayesian addition to the model would be to weight the likelihood that species $j$ is a predator of species $i$, considering that the closest relative of this predator is also a predator of $i$. It could account for part of the unexplained variation we found in our analysis, for instance by constraining the range of the diet for some large predators or by creating holes within the feeding range (Rall et al. 2011).}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{This is certainly an intriguing result coming out from our analysis. We also find this result interesting because it links to some of our previous work on persistence in metacommunities and our current work on the biogeography of body size. We also had a discussion with Neo Martinez at a previous workshop about this relationship, he was curious to see if his assumption of a linear relationship between the niche and the range of the diet was confirmed (Williams and Martinez, 2000). There are already a large number of figures in the paper (6) so we prefer not to add a new one, that could already be guessed from the Fig. 2. We however added the following discussion (at PXLX):}}

\textcolor{blue}{It appears at Fig. 2 that the feeding range increases with the body size of the predator. This result was quite general across datasets with a good fit of the predator-prey body size relationship, although with considerable variation in the slope of the relationship. It offers the possibility to compare empirical based estimates of the parameters to the original niche model of Williams (2011). For this specific dataset that the model for the centroid is $c_i = -1.34 + 0.66n_i$ and the average range ($\overline{r}_i=(r_{high,i} - r_{low,i})/2$) is $\overline{r}_i = 0.63 + 0.78n_i$. The original niche models assumed that $r_i$ scales linearly with connectance $C$ and the niche position, such that $r_i = 2Cn_i$. Even though the parameterization suggests a linear increase of generality with body size, the final number of preys in the diet for a given size will depend on the frequency distribution of body size. A large predator for instance could have a large feeding range, but only few species to find on and effectively appears as a specialist. This relationship will have to be investigated further, among several food webs (e.g. Digel et al. 2011), because the scaling of generality with trophic rank has several consequences on persistence (Gravel et al. 2011) and food web dynamics (e.g. Brose et al. 2006, Berlow et al. 2009).}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We fully agree with this result, it was also the central motivation for our investigations in a recent paper by Gravel et al. (2011, Ecology Letters). We hypothesized that this difference was the result of extinction-colonization dynamics, promoting the persistence of the most generalist species in local communities. It is however hard to figure out where to put this result in the current manuscript. We are currently working on a theory for metawebs, trying to develop a framework to improve inference of local web structure given the probability of the interactions in the metaweb. This approach considers the likelihood of an interaction between a pair of species given their co-occurrence andfavorable environmental conditions. This topic is however beyond the topic of the current paper. In fact, it goes the other way around. We need information on trait-matching to predict potential interactions in the metaweb (the topic of the current ms), and then a theory for sampling the metaweb.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do not find the corresponding point to correct. The lines following L214 refer to the paper by Eklof et al., and after a double checking of the paper it was found that most webs had between 3 and 6 dimensions, up to 9. We corrected accordingly.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{As stated
in the abstract, our method allows to ``infer the matrix of potential
interactions among a pool of species'', and does so regardless of whether one is
working at the local or regional scale. In the text, we give examples at both
these scales (locally in figures 2 and 3, regionaly in figure 5). We do agree
with the fact that additional information will make the predictions better; this
is described at length in the text, and an example of this (including
co-occurence along the depth gradient) is pictured in Fig. 5b. This is also
explicitly written in the discussion (L. XXX-XXX). We corrected the abstract and the last paragraph of the introduction to make clear that our metholody applies at both the local and metaweb scales.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We agree
that the fit of the model is only as strong as the relationship between prey and
predator body-size. This is the purpose of Fig. 3; this relationship is also
described in section 3.1 ``Predictive performance''. We made this point clear in the opening paragraph of the Discussion: 'However, because this allometric relationship is characteristic of predatory interactions, our method will likely not hold for other types of non-body-size structured interactions such as herbivory and parasitism'. We added also some cautionary remarks in the last paragraph of the introduction: 'The method is best suited for strongly size-structured food webs and will likely not hold for other types of non-body-size structured interactions. We therefore conclude on the future issues to generalize this approach to other types of trait matching models'.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The study of Rohr et al. (2010), does not allow to evaluate the parameters of a new species entering a local community, neither the metaweb (which is the object of the current study). It is therefore not possible to infer the potential links an immigrating species will do with the resident species. These methods also require a complete knowledge of the interactions in the community. Our method is consequently much more robust than previous methods to infer the parameters of the niche model. Based on these arguments, we believe that the method  will be used for instance to study the interactions in emerging communities following global changes.}}

@@

\medskip \textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We do agree that the best statistical model for this analysis should be a type 2 regression. We however deliberately used a type 1 regression for two reasons: i) we needed the R2 of the model to perform the analysis of predictive performance (Fig. 3). ii) we are not aware of any quantile regression that could account for uncertainty in the independent variable. We added a mention to this issue at LXXX.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{We modified the sentence to avoid amiguities. The metaweb gives interactions among a given set of species, wether at local or regional scales.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{See the above responses to previous comments.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{These are the parameters of the linear quantile regressions. The sentence was corrected accordingly.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{Whether the
correct prediction of absence or presence of an interaction is the most
interesting part of a model is ultimately a matter of personal taste, and
adequation to the study objectives. Given that (especialy when no other traits
than body size are included), this method tends to over-estimate the number of
links, we argue that correctly predicting absences of links is an extremely
important feature.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The choice of quantiles are left free to the user in the R code providing with this article, by default, we chose the most commonly used threshold of 5\% and 95\%. A threshold of 100\% would include all interactions, but would tend to overpredict the link density.}}

@@

\textcolor{blue}{\textbf{Response:}} \textit{\textcolor{blue}{The $c$ is
constrained by $n$ in the original niche model: it is drawn uniformly
between $r/2$ and $n$, with the expected value of $r$ being $2Cn$.}}

\textit{\textcolor{blue}{The fact that our model over-predict the number of
interactions is discussed in the manuscript (along with why, and how to overcome
it). However, the purposes of the two models are not the same. The niche model
allows to generate a distribution of network properties based only on
connectance and richness. We add allometric informations so as to be able to
estimate species-level interactions in addition to network properties. The
allometric relationshipss on which we rely are well documented. As for the fact
that other traits can be added, this is discussed in the manuscript at several
places, including a figure. }}
